Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-30 lloveras_2020_Albert.tex
..

%---------REMOVE THESE OPTIONS AND DEFs BEFORE SUMBISSION---------------------------------------
\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
                                         % ponen a disposición los colores ejemplificados aquí:
                                         % https://en.wikibooks.org/wiki/LaTeX/Colors
\def\diego#1{\textcolor{red}{#1}}
\def\albert#1{\textcolor{orange}{#1}}
\def\fede#1{\textcolor{ForestGreen}{#1}}
\def\temp#1{\textcolor{gray}{#1}}
\def\notebyalbert#1{\textcolor{blue}{NOTE: #1}}
%-----------------------------------------------------------------------------------------------

\begin{document}

\begin{article}

@@

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} images {of space} borne instruments, {differential emission measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework. {Two target} rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and {the {end of the} declining} phase of SC 24. The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis. We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt. We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves. {We also show that results of the latest version of the AWSoM model overal} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy. We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
\end{abstract}

\keywords{\albert{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}}

@@

{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global quiet-Sun corona. {DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}. More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs. Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base in order to maintain stable coronal loops}. In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Weather} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}. {The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation. As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.

@@

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. \\
In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs. They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious. This thermodynamic structure of the streamer have been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.

{For both target rotations, Figure \ref{carmaps_R_2082_2208} shows {latitude-longitude} maps of {the DEMT} measure $R$ defined by Equation \ref{R}, at the same three heights shown in Figures \ref{momento1} and \ref{momento2}. In most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found in the CHs of the target rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_R_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{{Carrington maps of the measure $R$ defined by Equation \ref{R}, for CR-2082 (left panels) and CR-2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. }
\label{carmaps_R_2082_2208}
\end{center}
\end{figure}

@@

{For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature. {Maps are shown} at the same three heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}. {Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model. Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic model.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
\caption{Carrington maps of density (left panels) and temperature (right panels) obtained with AWSoM model for the same three heights shown in Figure \ref{carmaps_demt_2082}.}
\label{carmaps_awsom_2082}
\end{center}
\end{figure}

{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$. Indeed, the top panels in Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208}, at height $1.025\,\mrsun$, clearly do not represent coronal conditions (although we include them here for completeness). When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs. Furthermore, for both target rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results. The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a visual comparison among them already reveals similar values of electron density and temperature in both models.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_awsom_2208} for CR-2208.}
\label{carmaps_awsom_2208}
\end{center}
\end{figure}

{Being highly axisymmtric target rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure. Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature. {The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded. In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle. Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red). In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-close boundary in both hemispheres.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
\caption{Longitude-averaged latitudinal dependence of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for target rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$. Dashed lines correspond to AWSoM results while solid line to DEMT. The vertical black line indicates the longitude-averaged latitudes of the open/closed magnetic boundary in both hemispheres.}
\label{perf_lat}
\end{center}
\end{figure}

{{Several details from Figure \ref{perf_lat} are worth being highlighted. Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208. The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much. In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend. {For comparison, note the behavior of $B_r$ in the CHs, increasing from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}

@@

To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines. For each field line leg, the results were then fit to Equations \ref{Nfit} and \ref{Tfit}{, considering only data points above heliocentric height $1.055\,\mrsun$. We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.  Legs of type 0 are not included for AWSoM, as in its current implementation it can not simulate down loops, a point we will discuss in the next section.}

@@

@@

{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary). The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}. The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}. For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$. {These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to DEMT in different magnetic structures.}}

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
\hline   
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

@@

{We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208. The first target belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24. The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme. As a result of the former, artifacts introduced by coronal dynamics are mitigated, and as a result of the latter, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid when compared to previous reconstructions. The MHD model used is here the latest version of the AWSoM component of the SWMF suite.}

@@

Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both target rotations, magnetic field lines of type 0, I and II are associated to increasingly outer {layers} of the equatorial streamer belt. Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} report in 3D quantitative detail how these progressively outer magnetic structures exhibit progressively decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both target rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.

>>>>

%-------------remove these two lines before submision--------------------------
\usepackage[usenames,dvipsnames]{xcolor} % Las opciones: [USENAMES,DVIPSNAMES] 
\def\albert#1{\textcolor{orange}{#1}}
%------------------------------------------------------------------------------

\begin{document}
\begin{article}

@@

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} images {of space} borne instruments, {differential emission measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework. {Two target} rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and {the {end of the} declining} phase of SC 24. The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis. We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt. We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves. {We also show that results of the latest version of the AWSoM model overall} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy. We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
\end{abstract}

\keywords{Solar Cycle, Observations; Corona, E; Corona, Structures; Corona, Models; Magnetohydrodynamics}

@@

{The combination of DEMT with global magnetic models provides insight} into the 3D thermodynamical structure of the global corona. {DEMT was first combined with a potential field source surface (PFSS) model by \citet{huang_2012} and \citet{nuevo_2013}. More recently,} \citet{lloveras_2017} combined DEMT with PFSS {models to study the thermodynamics of the global solar corona in specific magnetic structures for two target rotations selected from the last two solar minimum epochs. Also combining DEMT with a PFSS model,} \citet{maccormack_2017} developed a new DEMT product that estimates the energy input flux {required at the coronal base in order to maintain stable coronal loops}. In this article, {DEMT is first combined with the magnetic field of a magnetohydrodynamic (MHD) model.}

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space Wea\-ther Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}. {The only data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation. As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a global fashion.

@@

Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population \albert{in each case. In Section} \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.

@@

{{Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show that} the DEMT reconstruction of the streamer belt is characterized by relatively higher densities and temperatures in comparison to the CHs. They also show that the streamer belt region of CR-2082 was denser and colder than  that of CR-2208.} In the case of CR-2082, which belongs to the deep minimum epoch between {SCs 23 and 24}, the {low latitudes of the streamer belt are characterized by lower electron temperature than in its mid-latitudes.} A similar behavior is seen in CR-2208, belonging to the {end of the declining} phase of {SC 24}, but having a {somewhat less axisymmetric} structure this characteristic is not so obvious. This thermodynamic structure of the streamer has been reported for other solar minimum rotations in previous DEMT works \citep{lloveras_2017,nuevo_2013,vasquez_2010}.

Latitude-longitude maps of the score $R$ defined by Equation \ref{R} show that in most of the coronal volume of the DEMT grid the agreement between the tomographic and synthetic FBEs is $\lesssim 1\%$. The notable exception is to be found only in the CHs of the rotation {analysed} based on AIA data. A similar results was found in the two existing DEMT works based on data provided by the AIA instrument \citep{nuevo_2015,maccormack_2017}. This point is further discussed below in this section.

@@

{As described in Section \ref{awsom}, the AWSoM model includes an artificially thick TR, achieving coronal conditions above height $\approx 1.06\,\mrsun$. Results for the AWSoM model are shown here above that height. For both target rotations,} Figures \ref{carmaps_awsom_2082} and \ref{carmaps_awsom_2208} show latitude-longitude maps of the AWSoM electron density and temperature. {Maps are shown} at the two largest heights selected for visualization of the DEMT results in Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}. {Thick-black curves} indicate the magnetic open/closed boundaries based on the magnetic field of the AWSoM model. Visual inspection of these maps shows that the AWSoM model for both rotations is highly {axisymetric}, as the tomographic model.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
\caption{Carrington maps of density (left panels) and temperature (right panels) obtained with AWSoM model at heliocentric heights $1.065$ (top panels) and $1.105\,\mrsun$ (bottom panels).}
\label{carmaps_awsom_2082}
\end{center}
\end{figure}

{When compared to DEMT results (Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208}), the latitude-longitude maps of the AWSoM model for heights $1.065$ and $1.105\,\mrsun$ capture well the denser and hotter equatorial streamer belt surrounded by the less dense and colder CHs. Furthermore, for both rotations, the temperature maps show the low latitudes of the equatorial streamer belt to be characterized by lower temperatures than its mid-latitudes, as also seen in the DEMT results. The latitude-longitude maps of the AWSoM and DEMT results are shown in the same units and scales, so that a visual comparison among them already reveals similar values of electron density and temperature in both models.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_awsom_2082} for CR-2208.}
\label{carmaps_awsom_2208}
\end{center}
\end{figure}

{Being highly axisymmtric rotations, the longitude-averaged latitudinal {profile} of the results of both models is an informative way to compare their large-scale structure. Such comparison is shown in Figure \ref{perf_lat} at height $1.105\,\mrsun$, with top panels comparing electron density and mid panels electron temperature. {The longitude-averaged latitudinal profile of $B_r$ is shown in the bottom panels.} In these longitude-averaged profiles, longitudes containing ARs or low latitude CHs were excluded. In each panel the averaged latitudinal variation for the DEMT model is shown in solid-line style, while the result for the AWSoM model is shown in dashed-linesyle. Left panels show the comparison for CR-2082 (in blue) and right panels for CR-2208 (in red). In each panel the vertical black lines denote the corresponding longitude-averaged latitude of the open-closed boundary in both hemispheres.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2082_1105_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Br_2208_1105_2.pdf}
\caption{Longitude-averaged latitudinal variation of the electron density ({top panels}), {electron temperature ({middle panels})} and {radial magnetic field $B_r$ (bottom panels), for rotations} CR-2082 ({blue color, left panels}) and CR-2208 ({red color, right panels) at} $1.105\,\mrsun$. Dashed and solid lines indicate AWSoM and DEMT results, respectively. Vertical black lines indicate the longitude-averaged latitude of the open/closed magnetic boundary in both hemispheres.}
\label{perf_lat}
\end{center}
\end{figure}

{{Several details from Figure \ref{perf_lat} are worth being highlighted. Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208. The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much. In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend. {For comparison, note the behavior of $B_r$ in the CHs, increasing from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}

@@

To characterize the results of the AWSoM model in distinct magnetic structures, its results for electron density and temperature were traced along its magnetic field lines. For each field line leg, the results were then fit to Equations \ref{Nfit} and \ref{Tfit}{, considering only data points above heliocentric height $1.055\,\mrsun$. We then classified the traced legs into types I, II and III, according to the criteria described in Section \ref{trace}.  Legs of type 0 are not included for AWSoM \albert{as it currently can not simulate down loops, as discussed in Section \ref{discu}.}}

@@

{For rotation CR-2082, Figure \ref{histos_2082} shows the statistical distribution of the results of the DEMT (solid line-style) and AWSoM (dashed line-style) models traced along legs of type I, II and III (from top to bottom), as defined in Section \ref{trace}. From left to right: electron density at the lowest coronal height of the AWSoM model $\NCB\equiv\Ne(r=1.055\,\mrsun)$, electron density scale height $\lN$, and leg-averaged electron temperature $\aTm$. In each panel the median values $m$ are indicated. Figure \ref{histos_2208} shows the same analysis for rotation CR-2208.}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r }
\hline
Type    & \multicolumn{4}{c}{$\med(\NCB)$}             & \multicolumn{4}{c}{$\med(\lN)$} & \multicolumn{4}{c}{$\med(\avgTe)$} \\
        & \multicolumn{4}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{4}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{4}{c}{$[\MK]$} \\
\hline
CR-2082\\
I    & 1&15 &(\Mi&14\%)  &   7&5 &(\Pl&~8\%) &   1&25 &(\Mi&10\%) \\
II   & 0&99 &(\Mi&25\%)  &   9&9 &(\Mi&~2\%) &   1&36 &(\Mi&~2\%) \\
III  & 0&66 &(\Mi&17\%)  &   7&0 &(\Mi&~9\%) &   0&97 &(\Mi&~9\%) \\
\hline          
CR-2208\\
I    & 1&03 &(\Pl&~6\%)  &   9&7 &(\Mi&~8\%) &   1&55 &(\Mi&17\%) \\
II   & 0&79 &(\Pl&~9\%)  &  11&8 &(\Mi&14\%) &   1&58 &(\Mi&~8\%) \\
III  & 0&58 &(\Mi&~3\%)  &   8&9 &(\Mi&18\%) &   1&14 &(\Mi&18\%) \\
\hline   
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of leg defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are expressed relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

{For rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary). The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}. The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}. For rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$. {These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to DEMT in different magnetic structures.}}

@@

We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208. The former belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24. The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme (Section \ref{demt}). The MHD model used is here the latest version of the AWSoM component of the SWMF suite  (Section \ref{awsom}).

@@

Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations, magnetic field lines of type 0, I and II are associated with increasingly outer {layers} of the equatorial streamer belt. Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how these progressively outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency check for the changes implemented in the DEMT technique.

{{For both rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer. In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy. As a result, DEMT results based on AIA data {are less reliable CHs}. This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}. The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets. We are currently implementing an improved LDEM determination algorithm to to deal with this issue that will be used in a follow up article.}
